Using demographic accounts to enhance official population statistics

### 2021-09-28 article.tex

  \author*[1]{...}
  \author[2]{...}
  \author[1]{...} 
  \runningauthor{...}
  \affil[1]{...}
  \affil[2]{...}
  \title{...}
  \runningtitle{...}
  \subtitle{...}
  \abstract{...}
  \keywords{...}
  \classification[PACS]{...}
  \communicated{...}
  \dedication{...}
  \received{...}
  \accepted{...}
  \journalname{...}
  \journalyear{...}
  \journalvolume{..}
  \journalissue{..}
  \startpage{1}
  \aop
  \DOI{...}

@@

@@

\section{What is a demographic account}

\section{Why are demographic accounts useful?}

\section{Focus of paper}

@@

\section{Introduction} 
The Population Account for Greenland offers a set of coherent tables that allows calculations of all demographic measures at aggregated level.

\subsection{Corrections} 
Corrections are residuals, calculated to balance the sum of events in any period to explain change in the periodic population estimate.

P(t+1)≡P(t)+B(t)−D(t)+I(t)−E(t)+c(t)
, where t= time

>>>>

  \author*[1]{...}
  \author[2]{...}
  \author[1]{...} 
  \runningauthor{...}
  \affil[1]{...}
  \affil[2]{...}
  \title{ Using demographic accounts to enhance official population statistics  }
  \runningtitle{ Demographic accounts for Greenland }
  \subtitle{Demographic accounts for Greenland}
  \abstract{...}
  \keywords{...}
  \classification[PACS]{...}
  \communicated{...}
  \dedication{...}
  \received{...}
  \accepted{...}
  \journalname{...}
  \journalyear{...}
  \journalvolume{..}
  \journalissue{..}
  \startpage{1}
  \aop
  \DOI{...}

@@

\section{Introduction}

A demographic account is the demographic equivalent of a national account in economics. It is a comprehensive description of stocks and flows, linked together by accounting identities. Whereas a national account deals with economic quantities such as consumption, savings, investment, depreciation, and income, a demographic account deals with demographic quantities such as births, deaths, migration, and population. Demographic accounts and national accounts in fact share common intellectual origins. William Petty's political arithmetic, for instance, combined estimates of income and expenditure for 17th century England with estimates of population sizes. Richard Stone, one of the central figures in the development of modern national accounts also wrote extensively on social and demographic accounting, and devoted the final part of his Nobel Prize acceptance speech to subject of demographic accounts. REFERENCES.

National accounts and demographic accounts have, however, followed very different trajectories. National accounts are the centerpiece of official economic statistics. National accounting terms such as Gross Domestic Product or trade surplus are used by newspapers, politicians, and ordinary people. Although some demographic accounts, such as the \emph{World Population Prospects}, published by the United Nations Population Division, have become well-known, they are rarely described as demographic accounts. Neither the terminology nor the techniques of demographic accounting are widely used among professional statisticians and demographers.

In this paper we argue that the adoption of formal demographic accounting can help improve the clarity, consistency, and easy of use of official population statistics. We illustrate using the case of Greenland, which already publishes explicit demographic accounts. We describe the process of producing demographic accounts for Greenland, the benefits to producing demographic accounts, and the system for disseminating the results to potential users. In the final part of the paper, we discuss the implications for the production of population statistics in other countries.

\section{Greenland demographic data}

\section{Greenland demographic account}

The Population Account for Greenland offers a set of coherent tables that allows calculations of all demographic measures at aggregated level.

P(t+1) = P(t) + B(t) - D(t) + I(t) - E(t) + c(t)

\section{Dealing with discrepancies}

Corrections are residuals, calculated to balance the sum of events in any period to explain change in the periodic population estimate.

\begin{figure}
    \centering
    \includegraphics{}
    \caption{Caption}
    \label{fig:my_label}
\end{figure}

\section{Benefits of a demographic account}

\begin{itemize}
    \item data corrections (note - will discuss further below)
    \item understanding Greenland demographic system (eg movements to/from Denmark)
    \item transparency eg in forecasting
    \item make it easy for people to get data on demographic change, all in one place - and understand
    \item better scenario analysis
\end{itemize}

\section{Dissemination}

\begin{itemize}
    \item stat bank system
    \item ease of getting data
    \item common conventions on what the data should look like (to go with common software)
    \item how to disseminate uncertainty?
\end{itemize}

\section{Discussion (implications for other countries)}

\begin{itemize}
    \item can other countries emulate Greenland?: countries with good data vs countries with bad data
    \item why is it also useful in other countries
    \item can countries without population registers emulate greenland
    \item many agencies do accounting implicitly, adhoc
    denmark published from 1975-2004, then stopped ) :
    \item accounts for holland, faroe islands

\end{itemize}

What about countries without population registers?
\begin{itemize}
    \item a population count is a *model* of the population
    \item if a country does not have a population register but can estimate it, then they can still do an account; and reconcile via stat method
    \item need to be transparent but it best that can be produced
    \item we use National Accounts - even though they are badly imperfect
    \item in Copenhagen, demographic accounts where part of the demography mainstream
\end{itemize}

******************** NOTES *************************************

@@

FOCUS OF PAPER

@@
